handover

### 2021-01-29 inst/handover.Rmd
consistentification

---
title: "handover"
output: html_document
---

@@

Thus we see that in 26 cases, both reviewers answered "yes", in 18
both said "no".  The table also records partial responses that include
observations missed by one or both reviewers.  Responses missed by
both reviewers are uninformative and automatically rejected:
structural zeros, in `aylmer` terminology.  We first apply the Aylmer
test to assess whether the two reviewers give the same proportion of
"yes" responses:

@@

(Compare the McNemar test which gives an exact $p$-value of
$7/64\simeq 0.1094$).  We follow the previous workers and assume that
cases are missing at random and seek a likelihood function on
$\theta_{11},\theta_{10},\theta_{01},\theta_{00} subjet to
$\theta_{ij}\geq 0,\sum_{i,j \in\left\lbrace
0,1\right\rbrace}\theta_{ij}=1$.  Here "1" means "yes" and "0" means
"no", so $\theta_{01}$ is the probability of reviewer 1 responding
"no" and reviewer 2 responding "yes".

@@

### References

@@

### Package dataset

>>>>

---
title: "handover"
output: bookdown::html_document2
---

@@

Thus we see that in 26 cases, both reviewers answered "yes", in 18
<both said "no".  The table also records partial responses that include
observations missed by one or both reviewers.  Responses missed by
both reviewers are uninformative and automatically rejected:
structural zeros, in `aylmer` terminology.  We first apply the Aylmer
test to assess whether the two reviewers give the same proportion of
"yes" responses:

@@

(Compare the McNemar test which gives an exact $p$-value of
$7/64\simeq 0.1094$).  We follow the previous workers and assume that
cases are missing at random and seek a likelihood function on
$\theta_{11},\theta_{10},\theta_{01},\theta_{00}$ subject to
$\theta_{ij}\geq 0,\sum_{i,j \in\left\lbrace
0,1\right\rbrace}\theta_{ij}=1$.  Here "1" means "yes" and "0"
means "no", so $\theta_{01}$ is the probability of reviewer 1
responding "no" and reviewer 2 responding "yes".

@@

We can now consider the distribution of
$\psi=\theta_{10}/(\theta_{10}+\theta_{01})$ under the posterior
distribution induced by the complete cases:

```{r,samplepsi,message=FALSE,cache=TRUE}
jj <- rp(300000,H=handover)
head(jj)
psifun <- function(x){x[3]/(x[2]+x[3])}
logoddsfun <- function(x){log(x[2]/x[3])}
psi <- apply(jj,1,psifun)
log_odds <- apply(jj,1,logoddsfun)
psi_complete <- rbeta(length(psi),2,6)
```

We can now reproduce the four graphics given by Altham and Hankin:

Sample of $\psi=\theta_{10}/(\theta_{10}+\theta_{01})$ under the
posterior induced by the whole dataset (histogram), together with the
posterior distribution of $\psi$ induced by the complete cases only
(a beta distribution with parameters 2 and 6).

```{r histpsi,echo=FALSE,fig.cap="Sample of $\\psi=\\theta_{10}/(\\theta_{10}+\\theta_{01})$ under the posterior induced  by the whole dataset (histogram), together with the posterior distribution of $\\psi$ induced by the complete cases only (a beta distribution with parameters 2 and 6)"}
hist(psi,nclass=70,probability=TRUE,main=expression(paste("PDF of ",psi)))
p <- seq(from=0,to=1,len=100)
points(p,dbeta(p,2,6),type="l")
abline(v=psifun(handover_maxp),col="red",lwd=5)
segments(x0=0.5,y0=0,y1=1.5,col="blue",lwd=5)
legend("topright",lty=1,lwd=c(1,5,5),col=c("black","red","blue"),
       legend=c(
           "complete cases",
           expression(hat(psi) * " (complete cases)"),
           expression(psi * " = 0.5")
           ))
```

```{r qqplotpsi,echo=FALSE,fig.cap="Quantile-quantile plot of $\\psi=\\theta_{10}/(\\theta_{10}+\\theta_{01})$ under the posterior induced  by the whole dataset against the posterior distribution of $\\psi$ induced by the complete cases only (a beta distribution with parameters 2 and 6)",cache=TRUE}
par(pty='s')
qqplot(psi,psi_complete,asp=1,xlim=0:1,ylim=0:1)
abline(0,1)
```

```{r ecdfpsi,echo=FALSE,fig.cap="Empirical cumulative distribution function of $\\psi=\\theta_{10}/(\\theta_{10}+\\theta_{01})$ under the posterior induced  by the whole dataset, and that of $\\psi$ induced by the complete cases only (a beta distribution with parameters 2 and 6)",cache=TRUE}
plot(psi,seq_along(psi)/length(psi),type="l",col="black",xlab=expression(psi),ylab="quantile")
points(psi_complete,seq_along(psi_complete)/length(psi_complete),type="l",col="red")
legend("topleft",lty=1,col=c("black","red"),legend=c("whole dataset","complete cases"))
```

```{r logoddsqqplot,echo=FALSE,fig.cap="QQ plot of $\\phi=\\log(\\theta_{01}/\\theta_{10})$",cache=TRUE}
qqnorm(log_odds,main="QQ plot of log-odds")
abline(mean(log_odds),sd(log_odds))
```

Figures \@ref(fig:histpsi) to  \@ref(fig:logoddsqqplot) show different aspects of the dataset.

### References {-}

@@

### Package dataset {-}
